Density-dependent selection and the population ecology of relative fitness

### 2017-11-23 manuscript.tex
l

\title{Density-dependent selection with strictly relative competition}
%\author{Jason Bertram $^{1,\ast}$ \\ 
%Joanna Masel $^{1}$}

@@

\textit{Keywords}: r/K selection, absolute fitness, eco-evo, competition-colonization trade-off, fluctuating selection, storage effect.

@@

>>>>

\title{Density-dependent selection and the population ecology of relative fitness}
%\author{Jason Bertram $^{1,\ast}$ \\ 
%Joanna Masel $^{1}$}

@@

\textit{Keywords}: $r$/$K$ selection, absolute fitness, eco-evo, competition-colonization trade-off, fluctuating selection, storage effect.

@@

\begin{figure}
\centering
\includegraphics[scale=0.8]{LVvslottery.pdf}
\caption{\label{fig:Ksel} Blah}
\end{figure}
